---
title: "Exploratory Data Analysis Presentation"
author: "Felix Huang"
date: "`r Sys.Date()`"
output: 
  revealjs::revealjs_presentation:
    theme: solarized
    transition: zoom
    transitionSpeed: fast
bibliography: references.bib
csl: C:/Users/Felix Huang/Desktop/QTM 350/apa-5th-edition.csl
---

# Title Slide

## Exploratory Data Analysis of WDI Indicators

### Your Name

#### `r Sys.Date()`

------------------------------------------------------------------------

# Introduction

-   Overview of World Development Indicators (WDI)
-   Key indicators analyzed:
    -   GDP per Capita
    -   Life Expectancy
    -   Inflation Rate

------------------------------------------------------------------------

# Summary Statistics

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)

dataset <- read_csv("C:/Users/Felix Huang/Downloads/wdi.csv")

sum_stats <- dataset %>% 
  summarise(
    mean_gdp = mean(gdp_per_capita, na.rm = TRUE),
    median_gdp = median(gdp_per_capita, na.rm = TRUE),
    mean_life_exp = mean(life_expectancy, na.rm = TRUE),
    median_life_exp = median(life_expectancy, na.rm = TRUE),
    mean_inflation = mean(inflation_rate, na.rm = TRUE),
    median_inflation = median(inflation_rate, na.rm = TRUE)
  )

kable(sum_stats, caption = "Summary Statistics of Key Indicators") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))
```

------------------------------------------------------------------------

# GDP per Capita

-   Measures economic performance
-   Higher values indicate wealthier economies

```{r}
ggplot(dataset, aes(x = gdp_per_capita)) + 
  geom_histogram(bins = 30, fill = "steelblue", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "Distribution of GDP per Capita", x = "GDP per Capita (USD)", y = "Frequency")
```

------------------------------------------------------------------------

# Life Expectancy

-   Indicator of healthcare and living conditions
-   Longer life expectancy signals better public health

```{r}
ggplot(dataset, aes(x = life_expectancy)) + 
  geom_histogram(bins = 30, fill = "darkgreen", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "Distribution of Life Expectancy", x = "Life Expectancy (Years)", y = "Frequency")
```

------------------------------------------------------------------------

# Inflation Rate

-   Measures price stability in an economy
-   High inflation can reduce purchasing power

```{r}
ggplot(dataset, aes(x = inflation_rate)) + 
  geom_histogram(bins = 30, fill = "darkred", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "Distribution of Inflation Rate", x = "Inflation Rate (%)", y = "Frequency")
```

------------------------------------------------------------------------

# Conclusion

-   Summary of key findings
-   Implications for economic development
-   Future research directions

------------------------------------------------------------------------

# References

According to Smith (2020), GDP per capita is a key indicator of economic performance \citep{smith2020economic}. Similarly, Johnson and Lee (2019) discuss the importance of life expectancy as a measure of public health \citep{johnson2019life}.

------------------------------------------------------------------------

# Thank You!

-   Questions?
-   Contact: felix.huang\@emory.edu
